\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
a little more text

Observed in the \tess band, Sol d is a planet dominated by
clouds. \todo{Discuss how this problem is *hard* and how we need
large time baseline to disentangle clouds from continents, and even
then there are cloud features that are stationary, so hard to
tell apart. What we really need is multi-band photometry,
as suggested in \cite{Cowan2009}.}

>>>>

As we discussed above, light curve inversion is a hard problem,
and we have shown that this is true even when the solution is
known ahead of time. Presented with the top panel of Figure~\ref{fig:map}
(without the continent outlines),
an inhabitant of Sol d would be hard-pressed to identify that
as a map of their home planet. This is in part due to the biases
in our optimization, which we discussed above, but also due to the 
simple fact that the reflectance of Sol d is dominated---by far---by clouds.

\todo{Discuss how this problem is *hard* and how we need
large time baseline to disentangle clouds from continents, and even
then there are cloud features that are stationary, so hard to
tell apart. What we really need is multi-band photometry,
as suggested in \cite{Cowan2009}.}
